\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}

### 2021-03-18 papers/intro_paper/discussion.tex
changes in Table II, Sec. IV and V

\ab{We built a parameterized IMR waveform model, $\pSEOB$, that can 
measure the QNM complex frequencies of the remnant object formed \ab{through 
the merger of BHs with aligned or antialigned spins, thus extending  
previous work, which was limited} to non-spinning BHs~\cite{Brito:2018rfr}. 
The $\pSEOB$ model was recently used to infer the QNMs of some of the 
BBH's remnants detected by LIGO and Virgo during O3a~\cite{Abbott:2020jks}.}

We extended these results by analyzing GW events from the first and
second LIGO-Virgo observing runs and updated the joint measurements on
the fractional deviations in the frequency and damping time of the
least-damped QNM. As expected, the event providing the best constraint
on the least-damped QNM to be date continues to be GW150914 [see
\eqref{GW150914_delta}]. In addition, even in the most agnostic and
conservative scenario where we combine the information from different
events using an hierarchical approach, at $90\%$ credibility, we
constrain the frequency of the least damped QNM to be within $\sim
9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$
over the results reported in~\cite{Abbott:2020jks}. The constraints we
obtain on the frequencies and damping time of the least damped QNM are
compatible with the ones recently reported in
Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done
using only the post-merger part of the signal was analyzed.

>>>>

\ab{We have built a parameterized IMR waveform model, $\pSEOB$, that can 
measure the QNM complex frequencies of the remnant object formed \ab{through 
the merger of BHs with aligned or antialigned spins, thus extending  
previous work, which was limited} to non-spinning BHs~\cite{Brito:2018rfr}. 
The $\pSEOB$ model was recently used to infer the QNMs of some of the 
BBH's remnants detected by LIGO and Virgo during O3a~\cite{Abbott:2020jks}.}

\ab{After testing our method to infer the QNM frequencies with GR and non-GR synthetic-signal 
injections in Gaussian noise, we have applied it to LIGO and Virgo real data. 
We have analysed GW events in O1, O2 and O3a (a total of 4 new events) that were not examined in Ref.~\cite{Abbott:2020jks} 
with the $\pSEOB$ model (see Table~\ref{tab:qnm_o1o2_results}). After combining our new 
results with the other GW events in O3a investigated with our method~\cite{Abbott:2020jks}, 
we have obtained more stringent bounds on the dominant QNM $(\ell=2,m=2)$.}

\ab{More specifically,} as expected, the event providing the best constraint
on the least-damped QNM to be date continues to be GW150914 [see
\eqref{GW150914_delta}]. In addition, even in the most agnostic and
conservative scenario where we combine the information from different
events using an hierarchical approach, at $90\%$ credibility, we
constrain the frequency of the least damped QNM to be within $\sim
9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$
over the results reported in~\cite{Abbott:2020jks}. The constraints we
obtain on the frequencies and damping time of the least damped QNM are
compatible with the ones recently reported in
Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done
using only the post-merger part of the signal was analyzed.

### 2021-03-18 papers/intro_paper/results_lvc.tex
changes in Table II, Sec. IV and V

The LIGO-Virgo Collaboration recently released their testing GR
catalogue containing results for events observed
during O3a~\cite{Abbott:2020jks}. For the test that we here present, the results shown in Ref.~\cite{Abbott:2020jks} only include events which pass a threshold for the median \sout{redshifted} \ab{detector} total mass $\geq 90 \Mo$ and SNRs in the pre- and
post-merger regions $\geq 8$~\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis. The SNR values are listed in Table 4 of Ref.~\cite{Abbott:2020jks}}. 
%
The SNR threshold ensures that the signal contains sufficient information in both the inspiral and merger stages to break the degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$. Such strong degeneracy is present for low-SNR events with negligible higher-modes and for which only the post-merger is detectable rendering the measurement of $(\df{220}, \dtau{220})$ impossible for those cases.\rb{should we show an example where this degeneracy happens in the appendix? We can show a corner plot with $(\df{220}, \dtau{220}, M_{\rm total })$ for 21g in the appendix for example. And perhaps also for GW150914 for comparison.}\abhi{I would be fine with this. Perhaps we should have a discussion about how best to put it in the appendix, if we decide to.} \comment{AB: I would agree in showing the two plots that are at the end of the paper in a short Appendix B.}
On the other hand the total mass threshold $\geq 90 \Mo$ was employed due to the fact that this analysis is computationally expensive, and also because we expected these events to be the most promising for ringdown studies. However, since the SNR threshold alone should be sufficient for the analysis, for this paper we run the test on all the events listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and post-merger regions $\geq 8$, without imposing any mass threshold.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table for LVC values
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\input{table_lvc_results}
\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM, and the mass and spin of the remnant object estimated from 
the QNM frequencies \ab{using the $\pSEOB$ model.} \comment{AB: I would add the mass and spin of the remnant from NR fits, as well. The final mass should be multiplied by $(1+z)$. Correct?}}
\label{tab:qnm_o1o2_results}
\end{table}

>>>>

The LIGO-Virgo Collaboration recently released their testing GR
catalogue containing results for events observed
during O3a~\cite{Abbott:2020jks}. For the test that we here present, the results shown in Ref.~\cite{Abbott:2020jks} only include events which pass a threshold for the median \sout{redshifted} \ab{detector} total mass $\geq 90 \Mo$ and SNRs in the pre- and
post-merger regions $\geq 8$~\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis. The SNR values are listed in Table 4 of Ref.~\cite{Abbott:2020jks}}. 
%
The SNR threshold ensures that the signal contains sufficient
information in both the inspiral and merger stages to break the
degeneracy between the binary's total mass and the non-GR deviations
$(\df{220}, \dtau{220})$. Such strong degeneracy is present for
low-SNR events with negligible higher-modes and for which only the
post-merger is detectable rendering the measurement of $(\df{220},
\dtau{220})$ impossible for those cases. On the other hand the
total mass threshold $\geq 90 \Mo$ was employed due to the fact that
this analysis is computationally expensive, and also because we
expected these events to be the most promising for ringdown
studies. However, since the SNR threshold alone should be sufficient
for the analysis, for this paper we run the test on all the events
listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and
post-merger regions $\geq 8$, without imposing any mass threshold.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table for LVC values
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\input{table_lvc_results}
\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM \comment{AB: I believe it should be just $(2,2)$.}, and the mass and spin of the remnant object estimated from 
the QNM frequencies \ab{using the $\pSEOB$ model. We indicate with a star the GW events that were analysed in this paper, the other events were examined in Ref.~\cite{Abbott:2020jks}.} 
\comment{AB: I would add the mass and spin of the remnant from NR fits, as well. The final mass should be multiplied by $(1+z)$. Correct?}}
\label{tab:qnm_o1o2_results}
\end{table}
